\parrafo{jQuery}

\htmladdnormallink{jQuery}{http://jquery.com/} (\htmladdnormallink{Descarga la librería}{http://jquery.com/download/})

\cei{jQuery} is a cross-platform JavaScript library designed to simplify
the client-side scripting of HTML. 

\begin{itemize}
\item
It was released in January 2006
at BarCamp NYC by John Resig. 

\item
It is currently developed by a team of
developers led by Dave Methvin. 

\item
jQuery is the most popular JavaScript library in
use today

\item
jQuery's syntax is designed to make it easier 
\begin{itemize}
\item
to navigate a document,
\item
select DOM elements, 
\item
create animations, 
\item
handle events, and 
\item
develop Ajax applications. 
\end{itemize}

\item
The set of jQuery core features — DOM element selections, traversal
and manipulation — enabled by its selector engine (named "Sizzle"
from v1.3), created a new "programming style", fusing algorithms and
DOM-data-structures; and influenced the architecture of other JavaScript
frameworks like \wikip{YUI v3}{YUI\_Library} and \wikip{Dojo}{Dojo\_Toolkit}.
\item
\end{itemize}

\parrafo{How JQuery Works}

  \begin{itemize}
  \item
  Véase
  \htmladdnormallink{How jQuery Works}{http://learn.jquery.com/about-jquery/how-jquery-works/}
  \item
    \htmladdnormallink{https://github.com/crguezl/how-jquery-works-tutorial}{https://github.com/crguezl/how-jquery-works-tutorial} en GitHub
  \item
  \begin{verbatim}
  [~/javascript/jquery(master)]$ pwd -P
  /Users/casiano/local/src/javascript/jquery
  \end{verbatim}
  \item \htmladdnormallink{w3schools JQuery tutorial}{http://www.w3schools.com/jquery/default.asp}
  \end{itemize}

\begin{verbatim}
~/javascript/jquery(master)]$ cat index.html 
<!doctype html>
<html>
<head>
    <meta charset="utf-8" />
    <title>Demo</title>
</head>
<body>
    <a href="http://jquery.com/">jQuery</a>
    <script src="starterkit/jquery.js"></script>
    <script>
 
    // Your code goes here.
 
    </script>
</body>
</html>
\end{verbatim}

To ensure that their code runs after the browser finishes loading the document, many JavaScript programmers wrap their code in an onload function:

\begin{verbatim}
window.onload = function() { alert( "welcome" ); }
\end{verbatim}

Unfortunately, the code doesn't run until all images are finished downloading, including banner ads. To run code as soon as the document is ready to be manipulated, jQuery has a statement known as the ready event:

\begin{verbatim}
$( document ).ready(function() {
    // Your code here.
});
\end{verbatim}
For \verb|click| and most other events, you can prevent the default
behavior by calling 
\htmladdnormallink{event.preventDefault()}{http://api.jquery.com/event.preventdefault/}
in the event handler.
If this method is called, the default action of the event will not be triggered.
For example, clicked anchors will not take the browser to a new URL.

\begin{verbatim}
[~/javascript/jquery(master)]$ cat index2.html 
<!doctype html>
<html>
<head>
    <meta charset="utf-8" />
    <title>Demo</title>
</head>
<body>
    <a href="http://jquery.com/">jQuery</a>
    <script src="starterkit/jquery.js"></script>
    <script>
 
    $( document ).ready(function() {
        $( "a" ).click(function( event ) {
            alert( "The link will no longer take you to jquery.com" );
            event.preventDefault();
        });
    });
 
    </script>
</body>
</html>
\end{verbatim}
Borrowing from CSS 1–3, and then adding its own, jQuery offers a powerful set of tools for matching a set of elements in a document.

See jQuery \htmladdnormallink{Category: Selectors}{http://api.jquery.com/category/selectors/}.

Another common task is adding or removing a class.
jQuery also provides some handy effects.

\begin{verbatim}
[~/javascript/jquery(master)]$ cat index3.html 
<!doctype html>
<html>
<head>
    <meta charset="utf-8" />
    <style>
        a.test { font-weight: bold; }
    </style>
    <title>Demo</title>
</head>
<body>
    <a href="http://jquery.com/">jQuery</a>
    <script src="starterkit/jquery.js"></script>
    <script>
 
    $( document ).ready(function() {
        $( "a" ).click(function( event ) {
            $( "a" ).addClass( "test" );
            alert( "The link will no longer take you to jquery.com" );
            event.preventDefault();
            $( "a" ).removeClass( "test" );
            $( this ).hide( "slow" );
            $( this ).show( "slow" );
        });
    });
 
    </script>
</body>
</html>
\end{verbatim}
\begin{itemize}
\item
In JavaScript \verb|this| always refers to the {\it owner} of the function
we're executing, or rather, {\it to the object that a function is a method of}.

\item
When we define our function \verb|tutu()| in a page, its owner is the
page, or rather, the \verb|window| object (or \verb|global| object) of JavaScript. 

\item
An \verb|onclick| property, though, is owned by the HTML element it belongs to.

\item
The method
\htmladdnormallink{.addClass( className )}{http://api.jquery.com/addclass/}
adds the specified class(es) to each of the set of matched elements.

\verb|className| is a String containing 
one or more space-separated classes to be added to the class attribute of each matched element.

This method does not replace a class. It simply adds the class, appending
it to any which may already be assigned to the elements.
\item
The method \verb|.removeClass( [className ] )|
removes a single class, multiple classes, or all classes from each element in the set of matched elements.

If a class name is included as a parameter, then only that class will be
removed from the set of matched elements. If no class names are specified
in the parameter, all classes will be removed.

This method is often used with \verb|.addClass()| 
to switch elements' classes from one to another, like so:

\begin{verbatim}
$( "p" ).removeClass( "myClass noClass" ).addClass( "yourClass" );
\end{verbatim}

\end{itemize}

\input{chapter11/expressheroku.tex}

\input{chapter11/sinatraheroku.tex}

