\chapter{Rack, un Webserver Ruby Modular}
\label{chapter:rack}
\input{sinatra/rackup.tex}

\chapter{Primeros Pasos}
\input{sinatra/chapter1/sinatra.tex}

\chapter{Fundamentos}
\input{sinatra/chapter2fundamentos/fundamentos.tex}
\input{sinatra/chapter1/practicas.tex}

\chapter{Sinatra desde Dentro}
\input{sinatra/detrasdelascortinas.tex}


\chapter{Aplicaciones Modulares}
\input{sinatra/chapter4_modular_applications/chapter4_modular_applications.tex}

\chapter{Testing en Sinatra}
\begin{enumerate}
\item 
\htmladdnormallink{Build a Sinatra API Using TDD, Heroku, and Continuous Integration with Travis
by Darren Jones. Published December 9, 2013}{http://www.sitepoint.com/build-sinatra-api-using-tdd-heroku-continuous-integration-travis/} SitePoint
\item  Código del artículo anterior
\htmladdnormallink{}{git@github.com:crguezl/number_cruncher.git}
\item
\htmladdnormallink{Mini MiniTest Tutorial by Tim Millwood}{http://www.millwoodonline.co.uk/blog/mini-minitest-tutorial?utm_content=buffer1e8e1&utm_medium=social&utm_source=twitter.com&utm_campaign=buffer}

We'll use MiniTest::Spec, which is a functionally complete spec engine, to create a spec for a Hello World! Sinatra application. Firstly we create a folder 'spec' within the application directory. Within this, two files.


\begin{verbatim}
ENV['RACK_ENV'] = 'test'

require 'minitest/autorun'
require 'rack/test'
require_relative '../app'

include Rack::Test::Methods

def app
  Sinatra::Application
end
\end{verbatim}

The above code is to go into the file \verb|spec_helper.rb|. It sets up the initial setting for the test. We set the \verb|RACK_ENV| environment variable to 'test' then require '\verb|minitest/autorun|' for MiniTest, 'rack/test' because we are testing a rack based application and our application, in this case app.rb. The Rack::Test::Methods module is included to add a number of helper methods to allow the testing of rack applications. Finally we define the application as a Sinatra Application.
The next file \verb|app_spec.rb| will be our spec.
\begin{verbatim}
require_relative 'spec_helper'

describe 'Hello World' do

  it 'should have hello world' do
    get '/'
    last_response.must_be :ok?
    last_response.body.must_include "Hello world!"
  end
end
\end{verbatim}
Firstly the \verb|spec_helper| file is required, we then create a describe block to describe the 'Hello World' application. Within this a single behaviour. We run a get method against the root route and check the response is ok, and that the page includes the text 'Hello World!'.
\end{enumerate}

\chapter{CoffeeScript y Sinatra}
\input{sinatra/coffeescript.tex}

%%\chapter{Streaming}
%%\label{section:streaming}
%%\label{chapter:streaming}
%%\input{sinatra/streaming.tex}

%%\chapter{Web Sockets}
%%\label{chapter:websockets}
%%\input{sinatra/websockets.tex}

\chapter{Openid y Sinatra}
\input{sinatra/authentication.tex}

%%\chapter{Bootstrap your Web Application with Ruby and Sinatra}
%%\label{chapter:bootstrap}
%%\input{bootstrap/bootstrap.tex}


%%\chapter{Ajax in Sinatra}
%%\input{sinatra/ajaxysinatra.tex}

%%\chapter{Redis y Sinatra}
%%\label{chapter:redisysinatra}

%%\begin{enumerate}
%%\item 
%%\htmladdnormallink{Redis Quick Start}{http://redis.io/topics/quickstart}
%%\item 
%%\htmladdnormallink{How to Build a Shortlink App with Ruby and Redis
%%Charlie Somerville}{http://net.tutsplus.com/tutorials/ruby/how-to-build-a-shortlink-app-with-ruby-and-redis/}
%%en http://net.tutsplus.com/
%%\item 
%%\htmladdnormallink{Sinatra-Redis-Heroku-App}{https://github.com/crguezl/Sinatra-Redis-Heroku-App} en GitHub
%%\item 
%%\htmladdnormallink{sinatra-redis}{https://github.com/bmizerany/sinatra-redis}
%%extension
%%\item 
%%\htmladdnormallink{Redis Cloud}{https://devcenter.heroku.com/articles/rediscloud}
%%Redis Cloud is a managed cloud service for hosting and running your Redis dataset through its add-on for Heroku
%%\end{enumerate}

%%\chapter{MongoDB y Sinatra}
%%
%%
%%\begin{enumerate}
%%\item 
%%\htmladdnormallink{Getting Started with MongoDB}{http://docs.mongodb.org/manual/tutorial/getting-started/}
%%\item 
%%\htmladdnormallink{Mongoid}{http://mongoid.org/en/mongoid/}
%%\item 
%%\htmladdnormallink{MongoDB Ruby Driver Tutorial}{http://docs.mongodb.org/ecosystem/drivers/ruby/}
%%\item 
%%\htmladdnormallink{MongoDB Ruby Tutorial}{https://github.com/mongodb/mongo-ruby-driver/wiki/Tutorial}
%%en GitHub
%%\item 
%%\htmladdnormallink{Sinatra Recipes: MongoDB}{http://recipes.sinatrarb.com/p/databases/mongo}
%%\item 
%%Un ejemplo de 
%%spatial programming usando mongoid:
%%\htmladdnormallink{https://github.com/crguezl/spatial-ruby-openshift-quickstart}{https://github.com/crguezl/spatial-ruby-openshift-quickstart}.
%%Véase también:
%%\htmladdnormallink{Spatial apps on OpenShift PaaS using Ruby, Sinatra and MongoDB}{https://www.openshift.com/blogs/spatial-apps-on-openshift-paas-using-ruby-sinatra-and-mongodb}
%%
%%\end{enumerate}
%%
%%\chapter{Building Backbone.js Apps With Ruby, Sinatra, MongoDB and Haml}
%%Véase
%%\htmladdnormallink{Building Backbone.js Apps With Ruby, Sinatra, MongoDB and Haml}{http://addyosmani.com/blog/building-backbone-js-apps-with-ruby-sinatra-mongodb-and-haml/}
%%
\chapter{DataMapper y Sinatra}
\label{chapter:datamapperysinatra}
\input{sinatra/datamapper.tex}

%%\chapter{Sequel y Sinatra}
%%\label{chapter:sequelysinatra}
%%\input{sinatra/sequel.tex}
%%
%%\chapter{ActiveRecord y Sinatra}
%%\input{sinatra/activerecord.tex}
%%\input{sinatra/practicastinyurl.tex}

%\chapter{Google Plus y Sinatra}
%\input{sinatra/gplus.tex}

%%\chapter{Las Manos en la Masa: Nuestro Propio Blog Engine}

\chapter{Depuración en Sinatra}
\input{sinatra/depuracion.tex}

%\chapter{Despliegue en Heroku}
%\label{chapter:despliegueenheroku}
%\input{chapter11/heroku.tex}

\chapter{Envío de SMSs y Mensajes: Twilio y Clockworks}
\input{sinatra/sms.tex}

\chapter{Rest}
\htmladdnormallink{Uno! Use Sinatra to Implement a REST API.}{http://www.sitepoint.com/uno-use-sinatra-implement-rest-api/?utm_source=googleplus&utm_medium=post&utm_campaign=gp_0311}
by Dan Schaefer.  Published March 10, 2014

\chapter{Sinatra + Sprockets}

\begin{itemize}
\item
\htmladdnormallink{Sinatra + Sprockets}{http://blog.crowdint.com/2014/04/25/sprockets-sinatra.html?utm_source=blogpost&utm_medium=twitter&utm_campaign=sprocketssinatra-0425}
\item
\htmladdnormallink{Sprockets}{https://github.com/sstephenson/sprockets}
\item
\htmladdnormallink{https://github.com/crguezl/sinatra-sprockets-slim-backbone-example}{https://github.com/crguezl/sinatra-sprockets-slim-backbone-example}
\end{itemize}

\chapter{Sinatra::Flash}
\input{sinatra/flash.tex}

%%\chapter{Alternativas a Sinatra}
%%\input{sinatra/chapter_cuba/cuba.tex}

\chapter{Pruebas}
\begin{enumerate}
\item 
NetTuts+ tutorial: \htmladdnormallink{Testing Web Apps with Capybara and 
Cucumber}{http://net.tutsplus.com/tutorials/ruby/ruby-for-newbies-testing-web-apps-with-capybara-and-cucumber/}
Andrew Burgess on Aug 22nd 2011 with 22 Comments
\item 
\end{enumerate}

%%\chapter{Padrino}
%%\label{chapter:padrino}
%%\input{sinatra/padrino.tex}
%%
%%\chapter{Desarrolladores de Sinatra}
%%
%%\section{Konstantin Haase}
%%\begin{itemize}
%%\item 
%%\htmladdnormallink{Real Time Rack por Konstantin Haase}{http://confreaks.com/videos/727-rockymtnruby2011-real-time-rack} en 
%%\htmladdnormallink{http://confreaks.com/}{http://confreaks.com/}
%%\item 
%%El blog de 
%%\htmladdnormallink{Konstantin Haase}{http://rkh.im/} desarrollador al cargo de Sinatra
%%\item 
%%\htmladdnormallink{Konstantin Haase en GitHub}{https://github.com/rkh?tab=repositories}
%%\item 
%%\htmladdnormallink{Jose Mota}{https://github.com/josemota}
%%\end{itemize}
